%
%% Copyright (c) Members of the EGEE Collaboration. 2004-2010.
%% See http://www.eu-egee.org/partners for details on the copyright holders.
%% 
%% Licensed under the Apache License, Version 2.0 (the "License");
%% you may not use this file except in compliance with the License.
%% You may obtain a copy of the License at
%% 
%%     http://www.apache.org/licenses/LICENSE-2.0
%% 
%% Unless required by applicable law or agreed to in writing, software
%% distributed under the License is distributed on an "AS IS" BASIS,
%% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
%% See the License for the specific language governing permissions and
%% limitations under the License.
%
% -*- mode: latex -*-

\section{Credentials Handling}
\label{s:cs-auth-conn}

If we want to create new proxy certificate or \Eg delegate
credentials, we can use \CANL \verb'Certificate API'.
This part of API uses X509 authentication mechanism 
(uses openssl library now)

\subsection{Credentials API}
These are the functions of the \verb'Credentials API', all of them use
\verb'canl_ctx' as first parameter and \verb'canl_err_code' as a return
value, so we do not include them in following description:

\begin{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_new(canl_ctx, canl_cred *cred)\end{verbatim}
This function creates new structure (context) to hold credentials.
  \begin{itemize}
    \item param cred - new object will be retured to this pointer after
    success.
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_free(canl_ctx, canl_cred *cred)\end{verbatim}
  This function will free the credentials context, releasing
  all associated information.  The context must not be used after this call.
  \begin{itemize}
    \item param cred - credentials context to free 
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_ctx_set_cred(canl_ctx, canl_cred cred)\end{verbatim}
  This one sets users credentials to \CANL context
  \begin{itemize}
    \item param cred - credentials to set to global \CANL context
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_load_priv_key_file(canl_ctx, canl_cred cred, const 
char * file, canl_password_callback clb, void *pass)\end{verbatim}
  Load private key from specified file into credentials context.
  \begin{itemize}
    \item param cred - credentials which save private key to
    \item param file - file to load private key from
    \item param clb - A callback function which should return
    the password to the private key, if needed.
    \item param pass - User specified data that will be passed
    as is to the callback function.
  \end{itemize}
  \item \verb'canl_cred_load_chain(canl_ctx, canl_cred cred,'
  \verb' STACK_OF(X509) *chain)'
  This funcion loads certificate chain out of an openssl structure. The 
  chain usualy 
  consist of a proxy certificate and certificates forming
  chain of trust
  \begin{itemize}
    \item param cred - credentials context to set chain to
    \item param chain - openssl structre to load certificate chain from.
  \end{itemize}
  \item \verb'canl_cred_load_chain_file(canl_ctx, canl_cred cred,'
  \verb' const char * file)'
  This funcion loads certificate chain out of a file. The chain usualy 
  consist of a proxy certificate and certificates forming
  chain of trust
  \begin{itemize}
    \item param cred - credentials which save certificate chain to
    \item param file - file to load certificate chain from.
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_load_cert(canl_ctx, canl_cred cred, X509 *cert)\end{verbatim}
  This funcion loads user certificate out of an openssl structure.
  \begin{itemize}
    \item param cred - credentials context to set certificate to 
    \item param cert - openssl structure to load certificate from.
    \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_load_cert_file(canl_ctx, canl_cred cred, const char *file)\end{verbatim}
  This funcion loads user certificate out of a file.
  \begin{itemize}
    \item param cred - credentials which save certificate to
    \item param file - file to load certificate from.
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_set_lifetime(canl_ctx, canl_cred cred, const long lt)\end{verbatim}
  This function sets the lifetime for a certificate which is going to 
  be created
  \begin{itemize}
    \item param cred - credentials context
    \item param lt - lifetime in seconds
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_set_extension(canl_ctx, canl_cred cred, X509_EXTENSION *ext)\end{verbatim}
  This function sets the certificate extension to for the certificate 
  which is going to be created
  \begin{itemize}
    \item param cred - credentials context 
    \item param ext - openssl structure holding X509 certificate extension
  \end{itemize}
\item \begin{verbatim}
canl_err_code canl_cred_set_cert_type(canl_ctx, canl_cred cred, const enum canl_cert_type type)\end{verbatim}
  This function sets the certificate type to for the certificate
  which is going to be created
  \begin{itemize}
    \item param cred - credentials context
    \item param type - \CANL enum type ...\TODO type
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_sign_proxy(canl_ctx, canl_cred signer, canl_cred proxy)\end{verbatim}
  This function makes new proxy certificate based on information in 
  \textit{proxy} parameter. The new certificate is signed with private key 
  saved in \textit{signer}. A new certificate chain is saved 
  into \textit{proxy}
  \begin{itemize}
    \item param signer - credentials context which holds signer's certificate
    and key.
    \item param proxy - credentials context with a certificate 
    signing request, public key and user certifice; optionally lifetime,
    certificate type and extensions.
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_save_proxyfile(canl_ctx, canl_cred cred, const char * file)\end{verbatim}
  This function saves proxy certificate into a file
  \begin{itemize}
    \item param cred - credentials context with certificate to save 
    \item param file - save certificate into 
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_save_cert(canl_ctx, canl_cred cred, X509 **to)\end{verbatim}
  This function saves certificate into openssl object of type \textit{X509}
  \begin{itemize}
    \item param cred - credentials context with certificate to save
    \item param to - save certificate into
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_save_chain(canl_ctx, canl_cred cred, STACK_OF(X509) **to)\end{verbatim}
  This function saves certificate chain of trust with proxy 
  certificate into openssl object of type \textit{STACK\_OF(X509)}
  \begin{itemize}
    \item param cred - credentials context with certificate chain to save
    \item param to - save certificate into
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_new_req(canl_ctx, canl_cred cred, unsigned int bits)\end{verbatim}
  This function creates new certificate signing request after new key pair 
  is generated.
   \begin{itemize}
    \item param cred - credentials context, certificate signing request 
    is saved there
    \item param bits - key length
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_save_req(canl_ctx, canl_cred cred, X509_REQ **to)\end{verbatim}
  This function saves certificate signing request into openssl object of type \textit{X509\_REQ}
  \begin{itemize}
    \item param cred - credentials context with certificate request
    \item param to - save certificate request into
  \end{itemize}
  \item \begin{verbatim}
canl_err_code canl_cred_save_req(canl_ctx, canl_cred cred, X509_REQ **to)\end{verbatim}
  This function loads certificate signing request from openssl object of type \textit{X509\_REQ} into \CANL certificate context
  \begin{itemize}
    \item param cred - credentials context, cert. request will be stored there
    \item param to - load certificate request from
  \end{itemize}

\end{itemize}

\subsection{Make and Initialize New proxy certificate - example}
\TODO Do it

Include nesessary header files:
\begin{lstlisting}
#include <canl.h>
#include <canl_cred.h>
\end{lstlisting}


